---
title: "Project_2"
output: html_document
---


```{r}
library(dplyr)
library(readr)
library(stringr)
library(igraph)
library(dplyr)
library(ggplot2)
library(tm)
library(tidytext)
library(janeaustenr)
library(tidyr)
library(ggraph)
```

#Task 1

## 1. Use the solution from homework 1 question 3.1 as the adjacency matrix

The Adjacency Matrix code:

```{r}

#Read the data file
df_kw <- read.csv("Keyword_data - Keyword_data.csv", header = TRUE)

#Removing the first column and blank rows
df_kw <- subset(df_kw,select = -c(Title))
df_kw <- df_kw[!apply(df_kw == "", 1, all),]

#Creating a single combined vector of keywords
df_kw_row_list <- split(df_kw,1:nrow(df_kw))
kw_vector <- unlist(df_kw_row_list, use.names = FALSE)
kw_vector <- kw_vector[!is.na(kw_vector) & kw_vector != ""]
comb_vector <- unique(kw_vector)

#Creating Weighted Adjacency Matrix
df_to_mat <- matrix(df_kw)

weighted_adjacency_matrix = matrix(0,length(comb_vector),length(comb_vector))
rownames (weighted_adjacency_matrix) <- comb_vector
colnames(weighted_adjacency_matrix) <- comb_vector

#Populating the Weighted Adjacency Matrix
for(i in 1:nrow(df_kw)) {
    row <- df_kw[i,]
    row <- row[!is.na(row) & row != ""]
    for (j in 1:length(row)) {
      for (k in 1:length(row)) {
        if (j != k) {
        weighted_adjacency_matrix[row[j],row[k]] = weighted_adjacency_matrix[row[j],row[k]] + 1
        }
      }
    }
}
```

## 2. Read the adjacency matrix and convert it into a weighted network


```{r}
ig<- graph_from_adjacency_matrix(
  weighted_adjacency_matrix,
  mode =  ("undirected"),
  weighted = TRUE,
  diag = TRUE,
  add.colnames = NULL,
  add.rownames = NA
)
plot(ig)


```

## 3. Compute node degree and strength

```{r}


ig_deg <- degree(ig, mode="all")

ig_strength <- strength(ig,vids = V(ig))


```

## 4. Show the top 10 nodes by degree and top 10 nodes by strength

```{r}
df_degree<- data.frame(Degree = ig_deg)

#Top 10 nodes by degree
ig_degree_highest10 <- df_degree %>%  
  arrange(desc(ig_deg)) %>%
  head(10)

ig_degree_highest10
```
```{r}
df_strength<- data.frame(Strength = ig_strength)

#Top 10 nodes by degree
ig_strength_highest10 <- df_strength %>%  
  arrange(desc(ig_strength)) %>%
  head(10)

ig_strength_highest10
```

## 5. Show the top 10 node pairs by weight


```{r}
node_pair_weights = data_frame()
for (i in 1:length(rownames(weighted_adjacency_matrix)))
{
  for (j in 1:length(colnames(weighted_adjacency_matrix)))
  {
    if(j>i && weighted_adjacency_matrix[i,j]>0)
    {
      a = data_frame(keyword = paste(rownames(weighted_adjacency_matrix)[i],
                                    colnames(weighted_adjacency_matrix)[j], 
                                    sep =" - "), 
                    weight = (weighted_adjacency_matrix)[i,j])
      node_pair_weights = rbind(node_pair_weights,a)
    }
  }
}

highest_10_node_pairs_weight <- node_pair_weights %>%
  arrange(desc(weight)) %>%
  head(10)
highest_10_node_pairs_weight
```


## 6. Plot average strength on y-axis and degree on x-axis

```{r}

avg_strength <- mean(ig_strength)

graph_data <- data.frame(ig_deg,ig_strength)

ggplot(graph_data, aes(x = ig_deg, y = avg_strength))  +
  geom_point() +
  xlab("Degree")+
  ylab("Average Strength")
  ggtitle("Average Strength vs Degree")

```
# Task 2

#2.1 - Finding the frequency of words using stopwords

```{r}

data17 <- read_csv('2017.csv')
data18 <- read_csv('2018.csv')
data19 <- read_csv('2019.csv')
data20 <- read_csv('2020.csv')
data21 <- read_csv('2021.csv')

```

#For the year 2017
```{r}
data2017<- as.data.frame(data17['tweet'])
data2017_tokenized <- data2017 %>% unnest_tokens(word, 'tweet')
data2017_final <- data2017_tokenized %>% 
  group_by(word) %>%
  summarise(number=n())

data2017_final1 <- filter(data2017_final, !(word %in%  stopwords()))

data2017_final1

```

#For the year 2018

```{r}
data2018<- as.data.frame(data18['tweet'])
data2018_tokenized <- data2018 %>% unnest_tokens(word, 'tweet')
data2018_final <- data2018_tokenized %>% 
  group_by(word) %>%
  summarise(number=n())
data2018_final1 <- filter(data2018_final, !(word %in%  stopwords()))

data2018_final1
```

#For the year 2019

```{r}
data2019<- as.data.frame(data19['tweet'])
data2019_tokenized <- data2019 %>% unnest_tokens(word, 'tweet')
data2019_final <- data2019_tokenized %>% 
  group_by(word) %>%
  summarise(number=n())
data2019_final1 <- filter(data2019_final, !(word %in%  stopwords()))

data2019_final1
```

#For the year 2020

```{r}
data2020<- as.data.frame(data20['tweet'])
data2020_tokenized <- data2020 %>% unnest_tokens(word, 'tweet')
data2020_final <- data2020_tokenized %>% 
  group_by(word) %>%
  summarise(number=n())
data2020_final1 <- filter(data2020_final, !(word %in%  stopwords()))

data2020_final1

```

#For the Year 2021

```{r}
data2021<- as.data.frame(data21['tweet'])
data2021_tokenized <- data2021 %>% unnest_tokens(word, 'tweet')
data2021_final <- data2021_tokenized %>% 
  group_by(word) %>%
  summarise(number=n()) 
data2021_final1 <- filter(data2021_final, !(word %in%  stopwords()))

data2021_final1
```

## 2.2 --  Top 10 per each year by the highest value of word frequency

```{r}
data2017_final12 <- data2017_final1 %>% arrange(desc(number))
data2017_final12 <- head(data2017_final12,10)

data2018_final12<-  data2018_final1 %>% arrange(desc(number))
data2018_final12 <- head(data2018_final12,10)

data2019_final12<-  data2019_final1 %>% arrange(desc(number))
data2019_final12 <- head(data2019_final12,10)

data2020_final12<-  data2020_final1 %>% arrange(desc(number))
data2020_final12 <- head(data2020_final12,10)

data2021_final12<-  data2021_final1 %>% arrange(desc(number))
data2021_final12 <- head(data2021_final12,10)

```

##2.3 Histogram of word frequencies

```{r}
data2017_final12['Frequency']= round(data2017_final12['number']/sum(data2017_final12['number']),5)

ggplot(data2017_final12, aes(Frequency,fill=factor(2017))) + 
  geom_histogram(bins=15)
```
```{r}
data2018_final12['Frequency']= round(data2018_final12['number']/sum(data2018_final12['number']),5)

ggplot(data2018_final12, aes(Frequency,fill=factor(2018))) + 
  geom_histogram(bins=15)
```
```{r}
data2019_final12['Frequency']= round(data2019_final12['number']/sum(data2019_final12['number']),5)

ggplot(data2019_final12, aes(Frequency,fill=factor(2019))) + 
  geom_histogram(bins=15)
```

```{r}

data2020_final12['Frequency']= round(data2020_final12['number']/sum(data2020_final12['number']),5)

ggplot(data2020_final12, aes(Frequency,fill=factor(2020))) + 
  geom_histogram(bins=15)

```
```{r}
data2021_final12['Frequency']= round(data2021_final12['number']/sum(data2021_final12['number']),5)

ggplot(data2021_final12, aes(Frequency,fill=factor(2021))) + 
  geom_histogram(bins=15)

```

#2.4 Use Zipf’s law and plot log-log plots of word frequencies and rank for each year

```{r}
data2017_final112 <- data2017_final12 %>%  mutate(rank=row_number())

lm(log10(Frequency) ~ log10(rank), data = data2017_final112)

ggplot(data2017_final112, aes(rank, Frequency)) + 
  geom_abline(intercept = -0.5969, slope = -0.7054, 
              color = "red") +
  geom_line(size=1.5) +
  scale_x_log10() +
  scale_y_log10()
```

```{r}
data2018_final112 <- data2018_final12 %>%  mutate(rank=row_number())

lm(log10(Frequency) ~ log10(rank), data = data2018_final112)

ggplot(data2018_final112, aes(rank, Frequency)) + 
  geom_abline(intercept = -0.6929, slope = -0.5179, 
              color = "red", linetype = 2) +
  geom_line(size = 1.5) + 
  scale_x_log10() +
  scale_y_log10()
```


````{r}
data2019_final112 <- data2019_final12 %>%  mutate(rank=row_number())

lm(log10(Frequency) ~ log10(rank), data = data2019_final112)

ggplot(data2019_final112, aes(rank, Frequency)) + 
  geom_abline(intercept = -0.6448, slope = -0.6089, 
              color = "blue", linetype = 2) +
  geom_line(size = 1.5) + 
  scale_x_log10() +
  scale_y_log10()

```

```{r}
data2020_final112 <- data2020_final12 %>%  mutate(rank=row_number())

lm(log10(Frequency) ~ log10(rank), data = data2020_final112)

ggplot(data2020_final112, aes(rank, Frequency)) + 
  geom_abline(intercept = -0.6803, slope = -0.5425, 
              color = "red", linetype = 2) +
  geom_line(size = 1.5) + 
  scale_x_log10() +
  scale_y_log10()
```


```{r}
data2021_final112 <- data2021_final12 %>%  mutate(rank=row_number())

lm(log10(Frequency) ~ log10(rank), data = data2021_final112)

ggplot(data2021_final112, aes(rank, Frequency)) + 
  geom_abline(intercept = -0.6871, slope = -0.5295, 
              color = "red", linetype = 2) +
  geom_line(size = 1.5) + 
  scale_x_log10() +
  scale_y_log10()

```

#2.5 Create bigram network graphs for each year
```{r}
data2017_full <- data2017 %>%
  unnest_tokens(w1, tweet, token = "ngrams", n = 2) 

data2017_full_wording<- data2017_full %>%
  separate(w1, c("w1", "w2"), sep = " ")
data2017_filtered <-  data2017_full_wording %>%
  filter(!w1 %in% stopwords()) %>%
  filter(!w2 %in% stopwords())
data2017_filtered_number <- data2017_filtered %>% 
   count(w1, w2, sort = TRUE)
data2017_filtered_number<- data2017_filtered_number %>% drop_na()

data2017_filtered_graph<- data2017_filtered_number %>% filter(n>15) %>%
  
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(data2017_filtered_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "red") +
  geom_node_text(aes(label = name)) 


```

```{r}
data2018_full <- data2018 %>%
  unnest_tokens(w1, tweet, token = "ngrams", n = 2) 

data2018_full_wording<- data2018_full %>%
  separate(w1, c("w1", "w2"), sep = " ")
data2018_filtered <-  data2018_full_wording %>%
  filter(!w1 %in% stopwords()) %>%
  filter(!w2 %in% stopwords())
data2018_filtered_number <- data2018_filtered %>% 
   count(w1, w2, sort = TRUE)
data2018_filtered_number<- data2018_filtered_number %>% drop_na()

data2018_filtered_graph<- data2018_filtered_number %>% filter(n>15) %>%
  
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.8, "inches"))

ggraph(data2018_filtered_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "red") +
  geom_node_text(aes(label = name)) 

```

```{r}
data2019_full <- data2019 %>%
  unnest_tokens(w1, tweet, token = "ngrams", n = 2) 

data2019_full_wording<- data2019_full %>%
  separate(w1, c("w1", "w2"), sep = " ")
data2019_filtered <-  data2019_full_wording %>%
  filter(!w1 %in% stopwords()) %>%
  filter(!w2 %in% stopwords())
data2019_filtered_number <- data2019_filtered %>% 
   count(w1, w2, sort = TRUE)
data2019_filtered_number<- data2019_filtered_number %>% drop_na()

data2019_filtered_graph<- data2019_filtered_number %>% filter(n>15) %>%
  
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.8, "inches"))

ggraph(data2019_filtered_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "red") +
  geom_node_text(aes(label = name)) 

```

```{r}
data2020_full <- data2020 %>%
  unnest_tokens(w1, tweet, token = "ngrams", n = 2) 

data2020_full_wording<- data2020_full %>%
  separate(w1, c("w1", "w2"), sep = " ")
data2020_filtered <-  data2020_full_wording %>%
  filter(!w1 %in% stopwords()) %>%
  filter(!w2 %in% stopwords())
data2020_filtered_number <- data2020_filtered %>% 
   count(w1, w2, sort = TRUE)
data2020_filtered_number<- data2020_filtered_number %>% drop_na()

data2020_filtered_graph<- data2020_filtered_number %>% filter(n>15) %>%
  
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.8, "inches"))

ggraph(data2020_filtered_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "red") +
  geom_node_text(aes(label = name))

```


```{r}
data2021_full <- data2021 %>%
  unnest_tokens(w1, tweet, token = "ngrams", n = 2) 

data2021_full_wording<- data2021_full %>%
  separate(w1, c("w1", "w2"), sep = " ")
data2021_filtered <-  data2021_full_wording %>%
  filter(!w1 %in% stopwords()) %>%
  filter(!w2 %in% stopwords())
data2021_filtered_number <- data2021_filtered %>% 
   count(w1, w2, sort = TRUE)
data2021_filtered_number<- data2021_filtered_number %>% drop_na()

data2021_filtered_graph<- data2021_filtered_number %>% filter(n>25) %>%
  
  graph_from_data_frame()
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(data2021_filtered_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "red") +
  geom_node_text(aes(label = name)) 

```